Cosmological Hydrodynamic Simulations of Preferential Accretion in the SMBH of Milky Way Size Galaxies

### 2016-09-05 ms.tex
Removed all of Gas h258/h277 stuff; Focus of paper now on ChaNGa h258 (with small note about low res confirmation)
Most recent submission to Jillian and Kelly (7/24ish) with edits in Violet

\documentclass[manuscript]{aastex}

%-- Packages 
\usepackage[backref, breaklinks, colorlinks, citecolor=blue, linkcolor=magenta]{hyperref}

@@

\begin{abstract}\label{abs:abstractlabel}

Using the cosmological hydrodynamic simulation of a Milky Way-type (MW-type) Galaxy, we explore how a merger-rish assembly history affects the mass budget of the central SMBH. We examine a MW-mass halo characterized by several major mergers. We attempt to identify the importance of merger history on black hole accretion using a new high resolution simulation and advanced SPH code. This study is an extension of Bellovary et. al. 2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole is proportional to that accreted by the host galaxy halo. In this study, we find that contrarily a merger-rich galaxy will have a central SMBH preferentially fed by the merger gas fueling the system. Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH. In addition, the presence of mergers, particularly major mergers (q \textgreater 0.3), also helps funnel the low angular momentum gas more readily to the center of the galaxy. Our results imply that galaxy mergers play an important role in the feeding of the SMBH in merger-rich Milky Way-type galaxies.

\end{abstract}
\keywords{Black hole physics -- Galaxies: spiral -- Galaxies: kinematics and dynamics -- Methods: Numerical}

@@

It is clear that galaxy hosts grow through a variety of channels that depend on mass, environment, and interaction history. Therefore, we want to understand how these different galaxy evolutionary paths translate into SMBH fueling mechanisms, and see how they affect the fueling gas flowing into the SMBH itself. \cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH. Using a similar method as \cite{Bellovary2013}, this work examines the SMBH and galaxy fueling mechanisms of a Milky Way (MW) mass galaxy with a rich merger history. MW-type galaxies host SMBHs on the order of 10$^6$ $M_{\odot}$, which are likely the most common type of massive black hole, yet little is known about them or how they may grow \citep{Kormendy2013}. Through this examination, we hope to better understand the coevolution of SMBHs and their hosts in this class of galaxy.

In this study, we analyze the Milky Way-type galaxy, h258 (Figure \ref{h258face}), which has a history characterized by major mergers. Since this galaxy is similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the turbulent history that it results from. We will examine the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within this galaxy. By examining its assembly, and its SMBH's fueling, we can determine the accretion rate and gain further understanding about how SMBHs grow in galaxies like our own.

@@

% [NOTE TO SELF: Make/include merger trees. Ask Christina?] Can not do easily with current version parameters (halo switch turned off)

The cosmological simulations have been run using the smoothed particle hydrodynamics (SPH) N-body tree code: Charm N-body GrAvity solver, ChaNGa.

An initial DM-only, uniform resolution 50 comoving Mpc box determined what halo would be selected for zoom-in examination, including the halo examined in this paper. The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77. The halo h258 was chosen for its Milky Way-mass, 8.6 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and its active merger history. The halo has a virial mass defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 where h258 has virial mass of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$. A recent major merger characterizes the h258 halo at z=1. This ``zoom-in'' high resolution simulation was run on this galaxy and includes gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution. The simulation was run from z=150 to z=0.

%\subsection{High Resolution CHANGA Simulations}
While a previous, low resolution version of h258 was run using the Gasoline code, this newer, high resolution version of h258 includes the following properties: a spline force softening length of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$. Star particles are created with 30\% of their parent gas particle mass, allowing a maximum initial mass of 8100 $M_{\odot}$. Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total. The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.  At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.

Gas can reach a minimum temperature of $\sim$100 K, in the absence of cooling via molecular hydrogen or metals. The simulation includes stochastically-modeled star formation, and once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K), gas particles are eligible to form stars with an efficiency of c$^*$ = 0.1. Star particles form along the Kroupa initial mass function \citep{Kroupa2001}. Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}. In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation. SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities. Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}. A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}. Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}. Parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}. Given the strict adherence of this simulated galaxy with observations, we are confident that it reasonably represents growth in the galaxy and its SMBH. We exclude AGN feedback in these small to moderate mass-galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.

@@

Compared to the previous h258 simulation, the ChaNGa simulated h258 scales better and includes a new improved SPH formalism \citep{Keller2014}. The hydrodynamic treatment now includes a geometric density average\textemdash (P$_i$ + P$_j$)/($\rho_i \rho_j$) rather than P$_i$/$\rho_{i}^2$ + P$_j$/$\rho_{j}^2$ where P$_i$ and $\rho_i$ are the particle's pressure and density\textemdash in the force expression, in addition to the standard SPH density estimator \citep{Ritchie2001}. Adjusting the force expression diminishes tensions in the numerical surface due to shear flows, such as Kelvin-Helmholtz instabilities. We also apply a consistent and entropy-conserving energy equation to account for the modified force expression and correctly model strong shocks, such as Sedov blasts.

@@

The Amiga Halo Finder identifies and sets the virial radii in a simulation using an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004}. We select the primary halo to be the most massive galaxy at z=0 and locate the central SMBH. For this simulation, the primary halo in h258 had a final mass on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.

@@

The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 and the second at z $\sim$ 1.2. Despite its merger-rich history, gas accretion can be seen smoothly increasing the cumulative black hole mass throughout its evolution (Figure \ref{h258allmassgas}) Figure \ref{h258allmassgas} shows the cumulative SMBH mass in h258 as a function of time (lower axis) and redshift (upper axis). The black dashed line indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass. The blue dot-dashed line represents the gas mass accreted via unshocked gas, while the green solid line and red dashed line show the gas mass accreted through mergers and shocked gas, respectively. It is also worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed. This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}. Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1. It's clear from Figure \ref{h258allmassgas}, that unshocked gas makes up the majority of gas entering the galaxy at early times. However, the transitions between when smooth, unshocked accretion and mergers dominate is clearly distinguished. While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time ($\sim$ 2 Gyr) before clumpy gas once again dominates by z $\sim$ 1.5.

This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}). Figure \ref{hrh258stackfrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by gas origin. Blue, green, and red distinguish cold, clumpy, and shocked, respectively. The galaxy has a mass nearly half comprised of gas entering the galaxy through mergers (56 \%), with 36 \% of the gas entering through unshocked, smooth accretion. The smallest fraction of the total gas is comprised of shocked gas (8 \%). Unlike the galaxy, nearly three quarters of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (24 \%) is comprised of unshocked, smoothly accreted gas. Shocked gas makes up the last 2 \% of total gas entering the SMBH. \textbf{It is evident then that the SMBH more readily accretes gas gained through mergers.} This result is contrary to \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH and its host were nearly the same. Through our results, we find that lower mass galaxies can readily employ the physical effects of mergers to feed their SMBH.

To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy. Figure \ref{h258angmom} shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines), as expected; this statement is true regardless of the gas state.

Figure \ref{h258angmom_merger} explicitly shows that at the time of the merger, the lowest angular momentum gas entering the galaxy (solid lines) is merger-driven (green, solid line). This is reflected in the SMBH (green, dashed line) as nearly all the clumpy gas at this time funnels directly into the SMBH.

To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy. Figure \ref{hrh258angmom} shows a cumulative distribution of the gas particles' angular momentum as they enter the halo. The gas is again distinguished by their origin (Clumpy, cold, shocked being green, blue, and red, respectively.)and between gas that ends up in the SMBH (dashed line) or the galaxy (solid lines) at z=0. We find that the angular momentum of gas entering the SMBH is lower when comparing between types of gas. We also see that the lowest angular momentum gas is comprised of both clumpy and unshocked gas. This can be seen if we examine Figure \ref{hrh258angmom_merger2} which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the second merger. (Colors and linestyles as in Figure \ref{hrh258angmom}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum. There appears to be an influx of gas with low angular momentum feeding the black hole at this timestep that is not associated with the merger occurring at z $\sim$ 1.2. This may be attributed to the prior merger at z $\sim$ 1.8 (Figure \ref{hrh258angmom_merger1}) during and after which a large influx of low angular momentum gas enters the galaxy and SMBH. (Color and linestyles as in Figure \ref{hrh258angmom})

A lower resolution version of the galaxy h258 was run using the N-body code, Gasoline, like those simulations in \cite{Bellovary2013}. Despite being out-dated and utilizing different physics, an analysis of this low resolution h258 sees a SMBH with the same distinct preference for accreting gas, lending more credence to the results of this paper. We also note that while mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies, mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.

@@

\section{Conclusion}
This study examines the gas accretion onto the fully cosmological simulation of a Milky Way-size galaxy to redshift z $=$ 0, with major mergers characterizing its past. We trace the gas into the SMBH at its center and differentiate the gas accreted onto the galaxy and SMBH by origin. Gas gained through mergers is classified as ``clumpy'' gas and smoothly accreted gas is seperated into ``shocked'' and ``unshocked'' categories. Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.

A previous study by \cite{Bellovary2013} which analyized high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host. Contrary to these previous results, when we examined a galaxy with an active merger history, we determined that the SMBH at the center more readily accretes gas gained through mergers. This remained true both in an older low resolution simulation of the same galaxy as well as this current iteration. \textbf{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.}

@@

However, because this reult departs from the previous study, we consider that some of the physical processes affecting the galaxy with an active merger history accounts for the ready funneling of low angular momentum to the central region of the black hole.

While the examination of this extreme case of a galaxy with an active merger history depicts a class of galaxy with varying SMBH accretion methods, a further study of cases with varying merger histories is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion. It is clear through this study that the presence of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.

@@

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions}}}
\caption[]{Gas fractions of the gas particles accreted by the high resolution ChaNGA h258 by the main halo (left) and the SMBH (right), distinguished by type. Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively. Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable ($<$ 1 \%) within the SMBH.}
\label{hrh258stackfrac} 
\end{figure}

>>>>

\documentclass[manuscript]{aastex}
%-- Packages 
\usepackage[backref, breaklinks, colorlinks, citecolor=blue, linkcolor=magenta]{hyperref}
\usepackage[dvipsnames]{xcolor}

@@

\begin{abstract}\label{abs:abstractlabel}
\textcolor{violet}{
Using the cosmological hydrodynamic simulation of a Milky Way-type (MW-type) Galaxy, we explore how a merger-rish assembly history affects the mass budget of the central SMBH. We examine a MW-mass halo characterized by several major mergers. We attempt to identify the importance of merger history on black hole accretion using a new high resolution simulation and advanced SPH code. This study is an extension of Bellovary et. al. 2013, which analyzed the accretion of high mass, high redshift galaxies and their central black holes, and found that the gas content of the central black hole is proportional to that accreted by the host galaxy halo. In this study, we find that contrarily a merger-rich galaxy will have a central SMBH preferentially fed by the merger gas fueling the system. Through an investigation of the angular momentum of the gas entering the host and its SMBH, we determine that merger gas enters the galaxy with lower angular momentum compared to smooth accretion, partially accounting for the preferential fueling witnessed in the SMBH. In addition, the presence of mergers, particularly major mergers (q \textgreater 0.3), also helps funnel the low angular momentum gas more readily to the center of the galaxy. Our results imply that galaxy mergers play an important role in the feeding of the SMBH in merger-rich Milky Way-type galaxies.
}
\end{abstract}
\keywords{Black hole physics -- Galaxies: spiral -- Galaxies: kinematics and dynamics -- Methods: Numerical}

@@

\textcolor{violet}{
It is clear that galaxy hosts grow through a variety of channels that depend on mass, environment, and interaction history. Therefore, we want to understand how these different galaxy evolutionary paths translate into SMBH fueling mechanisms, and see how they affect the fueling gas flowing into the SMBH itself. \cite{Bellovary2013} compared simulations of three high mass, high redshift galaxies and found that while mergers and smooth accretion both efficiently build up galaxies, no particular method was more adept at feeding the SMBH. Using a similar method as \cite{Bellovary2013}, this work examines the SMBH and galaxy fueling mechanisms of a Milky Way (MW) mass galaxy with a rich merger history. MW-type galaxies host SMBHs on the order of 10$^6$ $M_{\odot}$, which are likely the most common type of massive black hole, yet little is known about them or how they may grow \citep{Kormendy2013}. Through this examination, we hope to better understand the coevolution of SMBHs and their hosts in this class of galaxy. 
}

\textcolor{violet}{
In this study, we analyze the Milky Way-type galaxy, h258 [Need a face on image of ChaNGa h258](Figure \ref{h258face}), which has a history characterized by major mergers. Since this galaxy is similar to the MW in virial mass, stellar mass, and circular velocity, without a deeper examination, we may not recognize the turbulent history that it results from. We will examine the origins of gas entering the SMBH and halo to look for clues about SMBH fueling within this galaxy. By examining its assembly, and its SMBH's fueling, we can determine the accretion rate and gain further understanding about how SMBHs grow in galaxies like our own.
}

@@

% [NOTE TO SELF: Make/include merger trees. Ask Christina?] Can not do easily with current version parameters (halo switch turned off)
\textcolor{violet}{
Using the smoothed particle hydrodynamics (SPH) N-body tree code: Charm N-body GrAvity solver, ChaNGa, an initial DM-only, uniform resolution 50 comoving Mpc box determined what halo would be selected for zoom-in examination, including the halo examined in this paper. The DM-only simulation assumed a WMAP Year 3 cosmology \citep{Spergel2007} with the following specifications: $\Omega _m$ = 0.24, $\Omega _{\Lambda}$ = 0.76, $H_0$ = 73 km/s, and $\sigma _8$ = 0.77. The halo h258 was chosen for its Milky Way-mass, 8.6 $\times$ 10$^{11}$  M$_{\odot}$, at z=0 and its active merger history. The halo has a virial mass defined relative to a critical density, $\rho _c$, where $\rho / \rho _c$ = 100 where h258 has virial mass of $M_{\rm vir} = 7 \times 10^{11} M_{\odot}$. A recent major merger characterizes the h258 halo at z=1. This ``zoom-in'' high resolution simulation was run on this galaxy and includes gas and star particles using the volume renormalization of \cite{Katz1993}, resimulating only a few virial radii from the main halo at the highest resolution. The simulation was run from z=150 to z=0.  
}

%\subsection{High Resolution CHANGA Simulations}
\textcolor{violet}{
While a previous, low resolution version of h258 was run using the Gasoline code, this newer, high resolution version of h258 includes the following properties: a spline force softening length of 174 pc and initial gas particle masses of $2.7 \times 10^4 M_{\odot}$. Star particles are created with 30\% of their parent gas particle mass, allowing a maximum initial mass of 8100 $M_{\odot}$. Each galaxy contains about 5 million DM particles inside the virial radius at z=0 and over 14 million DM, star, and gas particles total. The resolution of both force and mass in these simulations is comparable to the ``Eris'' simulation which has one of the highest resolutions for an N-body+SPH cosmological simulation of a Milky Way-mass galaxy so far produced.  At z=9, a uniform UV background is applied to simulate the cosmic reionization energy in a variation of \cite{Haardt2012}.
}
\textcolor{violet}{
Gas can reach a minimum temperature of $\sim$100 K, in the absence of cooling via molecular hydrogen or metals. The simulation includes stochastically-modeled star formation, and once the density threshold and temperature satisfy conditions for star formation (10.0 amu cm$^{-3}$; T \textless 10$^4$ K), gas particles are eligible to form stars with an efficiency of c$^*$ = 0.1. Star particles form along the Kroupa initial mass function \citep{Kroupa2001}. Supernova feedback releases $10^{51}$ ergs of thermal energy and affects a ``blastwave'' radius determined by the equations of \cite{Ostriker1988}. In the affected region, cooling turns off for a time relative to the expansion phase of the SN remnant also determined by the blastwave equation. SN Ia and II from \cite{Thielemann1986} and \cite{Woosley1986} are adopted, respectively, and implemented through the \cite{Raiteri1996} method, which uses the stellar lifetime calculations of the Padova group \citep{Alongi1993, Bressan1993, Bertelli1994} to describe stars with varying metallicities. Both the supernova ``blastwave'' radius and supernova (Ia and II) prescriptions are described in detail by \cite{Stinson2006}. A low-temperature extension to the cooling curve is used to trace metals \citep{Bromm2001}. Simulated galaxies are shown to conform with the observed Tully-Fisher relation \citep{Governato2009}, the size-luminosity relation \citep{Brooks2011}, and the mass-metallicity relation \citep{Brooks2007}, in addition to having realistic matter distributions and baryon fractions \citep{Governato2009a,Guedes2011}. Parameter and resolution choices described above allow the galaxies to adhere to the stellar-mass-halo-mass relation at z=0 and maintain a realistic period of star formation \citep{Moster2010,Munshi2013,Brooks2007,Maiolino2008}. Given the strict adherence of this simulated galaxy with observations, we are confident that it reasonably represents growth in the galaxy and its SMBH. We exclude AGN feedback in these small to moderate mass-galaxies; however, we have determined that has little effect on the global properties of the galaxy and SMBH.
}

@@

\textcolor{violet}{
Compared to the previous h258 simulation, the ChaNGa simulated h258 scales better and includes a new improved SPH formalism \citep{Keller2014}. The hydrodynamic treatment now includes a geometric density average\textemdash (P$_i$ + P$_j$)/($\rho_i \rho_j$) rather than P$_i$/$\rho_{i}^2$ + P$_j$/$\rho_{j}^2$ where P$_i$ and $\rho_i$ are the particle's pressure and density\textemdash in the force expression, in addition to the standard SPH density estimator \citep{Ritchie2001}. Adjusting the force expression diminishes tensions in the numerical surface due to shear flows, such as Kelvin-Helmholtz instabilities. We also apply a consistent and entropy-conserving energy equation to account for the modified force expression and correctly model strong shocks, such as Sedov blasts. 
}

@@

\textcolor{violet}{
The Amiga Halo Finder identifies and sets the virial radii in a simulation using an overdensity criterion for a flat universe \citep{Knebe2001,Knollmann2009,Gill2004}. We select the primary halo to be the most massive galaxy at z=0 and locate the central SMBH. For this simulation, the primary halo in h258 had a final mass on the order of $10^{12} M_{\odot}$ and a formation redshift of z$\sim$4.  
}

@@

\textcolor{violet}{
The galaxy h258 is characterized by two major mergers; the first occurs at z $\sim$ 1.8 and the second at z $\sim$ 1.2. Despite its merger-rich history, gas accretion can be seen smoothly increasing the cumulative black hole mass throughout its evolution (Figure \ref{hrh258allmassgas}) Figure \ref{hrh258allmassgas} shows the cumulative SMBH mass in h258 as a function of time (lower axis) and redshift (upper axis). The black dashed line indicates the total cumulative BH mass (including both mass from gas and BH mergers), while the black solid line indicates the total accreted gas mass. The blue dot-dashed line represents the gas mass accreted via unshocked gas, while the green solid line and red dashed line show the gas mass accreted through mergers and shocked gas, respectively. It is also worthwhile to point out that the largest part of the mass budget at high redshift is not gas at all, but other black holes that have merged with the SMBH seed. This has important implications for gravitational wave astronomy, increasing the event rate for SMBH assembly at high redshifts \citep{Holley-Bockelmann2010}. Aside from this early BH assembly, the largest gain in SMBH mass comes from gas associated with the major mergers between z $\sim$ 2 and z $\sim$ 1. It's clear from Figure \ref{hrh258allmassgas}, that unshocked gas makes up the majority of gas entering the galaxy at early times. However, the transitions between when smooth, unshocked accretion and mergers dominate is clearly distinguished. While clumpy gas (green) dominates at the earliest time, unshocked gas (blue) overtakes it for a short time ($\sim$ 2 Gyr) before clumpy gas once again dominates by z $\sim$ 1.5. 
}
\textcolor{violet}{
This low redshift transition to a clumpy gas preference results in the large fraction of clumpy gas seen in the SMBH (Figure \ref{hrh258stackfrac}). Figure \ref{hrh258stackfrac} depicts the fractions of total gas in the galaxy (a) and the SMBH (b) at z=0, again differentiated by gas origin. Blue, green, and red distinguish cold, clumpy, and shocked, respectively. The galaxy has a mass nearly half comprised of gas entering the galaxy through mergers (56 \%), with 36 \% of the gas entering through unshocked, smooth accretion. The smallest fraction of the total gas is comprised of shocked gas (8 \%). Unlike the galaxy, nearly three quarters of the gas accreted by the central SMBH was gas accreted via mergers, while only a quarter (24 \%) is comprised of unshocked, smoothly accreted gas. Shocked gas makes up the last 2 \% of total gas entering the SMBH. \textbf{It is evident then that the SMBH more readily accretes gas gained through mergers.} This result is contrary to \cite{Bellovary2013} which found that the fractions of gas comprising the SMBH and its host were nearly the same. Through our results, we find that lower mass galaxies can readily employ the physical effects of mergers to feed their SMBH.
}

\textcolor{violet}{
To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy. Figure \ref{hrh258angmom} shows that gas entering the SMBH (dashed lines) has an overall lower angular momentum than gas entering galaxy (solid lines), as expected; this statement is true regardless of the gas state. 
}

\textcolor{violet}{
Figure \ref{hrh258angmom_merger1} explicitly shows that at the time of the first merger, the lowest angular momentum gas entering the galaxy (solid lines) is merger-driven (green, solid line). This is reflected in the SMBH (green, dashed line) as nearly all the clumpy gas at this time funnels directly into the SMBH.
}

\textcolor{violet}{
To better understand the apparent preference for merger-accreted gas, we examine the angular momentum of each type of gas at the moment it enters the galaxy. Figure \ref{hrh258angmom} shows a cumulative distribution of the gas particles' angular momentum as they enter the halo. The gas is again distinguished by their origin (Clumpy, cold, shocked being green, blue, and red, respectively.)and between gas that ends up in the SMBH (dashed line) or the galaxy (solid lines) at z=0. We find that the angular momentum of gas entering the SMBH is lower when comparing between types of gas. We also see that the lowest angular momentum gas is comprised of both clumpy and unshocked gas. This can be seen if we examine Figure \ref{hrh258angmom_merger2} which shows the cumulative distribution of the angular momentum of the incoming gas particles at the time of the second merger. (Colors and linestyles as in Figure \ref{hrh258angmom}.) Figure \ref{hrh258angmom_merger2} explicitly shows that the gas ending up in the SMBH enters with the lowest angular momentum. There appears to be an influx of gas with low angular momentum feeding the black hole at this timestep that is not associated with the merger occurring at z $\sim$ 1.2. This may be attributed to the prior merger at z $\sim$ 1.8 (Figure \ref{hrh258angmom_merger1}) during and after which a large influx of low angular momentum gas enters the galaxy and SMBH. (Color and linestyles as in Figure \ref{hrh258angmom}) 
}

\textcolor{violet}{
A lower resolution version of the galaxy h258 was run using the N-body code, Gasoline, like those simulations in \cite{Bellovary2013}. Despite fundamental differences in the hydrodynamic implementation and gas physics included, an analysis of this low resolution h258 results in a SMBH with the same distinct preference for accreting gas. The broad consistency between the low and high resolution simulation of the same galaxy indicates that the large scale gravitational dynamics could be main driver of the SMBH fueling in this case. We also stress that that while major mergers may not be the only physical mechanisms by which gas can be funneled into the centers of galaxies (the previous study being a strong example of this), mergers between galaxies clearly play an important role when considering the gas accretion of SMBHs.
}

@@

\section{Conclusion}
\textcolor{violet}{
This study examines the gas accretion onto the fully cosmological simulation of a Milky Way-size galaxy to redshift z $=$ 0, with major mergers characterizing its past. We trace the gas into the SMBH at its center and differentiate the gas accreted onto the galaxy and SMBH by origin. Gas gained through mergers is classified as ``clumpy'' gas and smoothly accreted gas is seperated into ``shocked'' and ``unshocked'' categories. Our goal is to determine what types of gas are primarily feeding the SMBH and the galaxies of this class, and to determine what effects the merger history of a galaxy may have on these processes.
}

\textcolor{violet}{
A previous study by \cite{Bellovary2013} which analyized high mass, high redshift galaxies and found the gas composition of the SMBHs mirror their host. Contrary to these previous results, when we examined a galaxy with an active merger history, we determined that the SMBH at the center more readily accretes gas gained through mergers. This remained true both in an older low resolution simulation of the same galaxy as well as this current iteration. \textbf{In both the low and high resolution cases, we see a significant increase in the clumpy gas accreted by the SMBH compared to its host.} 
}

@@

\textcolor{violet}{
However, because this reult departs from the previous study, we consider that some of the physical processes affecting the galaxy with an active merger history accounts for the ready funneling of low angular momentum to the central region of the black hole. 
}
\textcolor{violet}{
While the examination of this extreme case of a galaxy with an active merger history depicts a class of galaxy with varying SMBH accretion methods, a further study of cases with varying merger histories is required to begin understanding the broad spectrum of Milky Way-mass galaxy accretion. It is clear through this study that the presence of major mergers can play an important role in the final compositions of central SMBHs, but the question of how important these mergers are remains to be seen.
}

@@

\begin{figure}
\centerline{\resizebox{0.75\hsize}{!}{\includegraphics[angle=0]{hrh258_stackbarfractions_good}}}
\caption[]{Gas fractions of the gas particles accreted by the high resolution ChaNGA h258 by the main halo (left) and the SMBH (right), distinguished by type. Blue, green, and red distinguish gas gained through unshocked gas, gained through mergers, and gas shocked upon entry, respectively. Yellow indicates gas that existed within the main halo upon formation; this ``early'' gas is negligable ($<$ 1 \%) within the SMBH.}
\label{hrh258stackfrac} 
\end{figure}
